### 2018-09-06 introduction.tex
which was is pointless verbage
MSBR should probably be introduced earlier, but its ok... as is, seems alright.. but should be its own paragraph
word order

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor which was developed at \gls{ORNL} 
in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
included \glspl{MSR} among the six most promising advanced reactor concepts for 
further research and development. 
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmutes into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.

>>>>

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
in the 1950s and operated in the 1960s. More recently, the \gls{GIF}  
included \glspl{MSR} among the six most promising advanced reactor concepts for 
further research and development. 
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}.

The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmutes into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.
